%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Shahwar}{Saleem}{ \urlstyle{Well Balanced Combination of Data Science and Software Engineering} 
\href{mailto:saleemshahwar@gmail.com}{saleemshahwar@gmail.com} | 226.220.7123}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}
\descript{MEng in Computer Engineering}
\location{August 2018 | Waterloo, ON \\ Cum. GPA: 89\%}
\sectionsep


\subsection{University of \\ Engineering and \\Technology}
\descript{BE in Computer Engineering}
\location{August 2013 | Lahore, Pakistan \\ Cum. GPA: 85\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/shahwar9}{\custombold{shahwar9}} \\
LinkedIn://  \href{https://www.linkedin.com/in/shahwar-saleem-050ba93a/}{\custombold{shahwarsaleem}} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Software Engineering}
Tools of Software Engineering \\
Algorithm Design and Analysis\\
Safety Critical Embedded Systems \\
Operating Systems \\
Computer Programming Languages \\
Data Structures \\
Computer Networks \\
Data Bases \\
\sectionsep

\subsection{Data Science}
Knowledge Modelling and Analysis \\
Tools of Intelligent Systems Design \\
Research Topics: Machine Learning \\
Text Analytics (NLP) \\
Deep Learning Specialization (Coursera)
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
\location{Over 5000 lines:}
\textbullet{} C \textbullet{} Python \textbullet{} JavaScript \textbullet{} Matlab \\
\textbullet{} \LaTeX\ \\ 
\location{Over 1000 lines:}
\textbullet{} Java \textbullet{} MySQL \textbullet{} C++
\sectionsep
\subsection{Tools}
\textbullet{} ROS \textbullet{} RASA \textbullet{}  Keras \textbullet{} React.js \\ \textbullet{} TensorFlow 
\textbullet{} GraphQL \textbullet{} Git \\ 
\textbullet{} JIRA \textbullet{} Slack\\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.63\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Pronavigator.io}
\descript{| Software Engineer (Machine Learning) }
\location{August 2018 - Present | Kitchener, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Prepared a research report and an example model to show that Fully Connected Neural Networks perform better than SVMs because of increased number of classes every day. Executed migration which saved significant servers cost per month and gained a huge performance increase. 

\item Improved the machine learning pipeline by implementing a Confusion Matrix tailored to text classification needs of NLU engine of Pronavigator. This provided a sight into correlations between different kinds of user messages.

\end{tightemize}
\sectionsep

\runsubsection{WISE Lab, UWaterloo}
\descript{| Graduate Research Assistant }
\location{May 2017 – Apr 2018 | Waterloo, ON}
\begin{tightemize}

\item Delivered successful autonomous stack of ROS/QNX (OS layers) on ARM based architecture after porting on newly made development boards called H3 by Renesas. Lead Autonmoose Integration team in CES'17. 

\item Improved Autonomous vehicle stack by implementing different components in ROS. Components like system monitor, risk monitor were a part of my contributions. 

\item Used Neural Networks to detect camera occlusion on Autonomous Vehicle. Occlusion detection was reported to a ROS based architecture to warn system about non-friendly environment/situations for vehicle safety. The results were used in publication.

\end{tightemize}
\sectionsep

%\runsubsection{Stowk, INC}
%\descript{| Machine Learning Engineer}
%\location{Sept 2016 - Aug 2017 | San Francisco Bay Area (Remote)}
%\begin{tightemize}
%\item  Design, experiment and maintenance of price prediction models based on RFs and NNs. Hands on experience with training neural networks for price prediction.
%\item Architecture design of React Native app for Stowk. Also worked on GraphQL based API backend.\end{tightemize}
%\sectionsep

\runsubsection{Mentor Graphics Corporation}
\descript{| Software Engineer}
\location{Oct 2013 - May 2016 | Lahore, Pakistan}
\begin{tightemize}

\item Improved visualization of processes on a multi-core architecture in RTOS by implementing a feature called Kernel Awareness. 

\item Experienced developing different device drivers for Nucleus RTOS. (I2C, SPI, LCD, CAN etc drivers for ARM \& PPC Architectures)

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\runsubsection{Waterloo Intelligent Systems Engineering (WISE) Lab}
\descript{| Co-Author}
\location{Jan 2018}
\textit{"An Automated Vehicle Safety Concept Based on Runtime Restriction of the Operational Design Domain"} , 2018 IEEE Intelligent Vehicles Symposium

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2016 - 2018	     & Graduate Research Studentship - University of Waterloo  \\
2016 - 2018	     & International Master's Student Award - University of Waterloo\\
2009 - 2013	     & National Talent Scholarship from Government of Pakistan\\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Graduate Projects} 

\begin{tabular}{rll}



2018   &  Fake News Challenge Phase 1   &  \href{https://github.com/shahwar9/fakenewschallenge}{\custombold{Github}}\\
2017   &  Prediction of Yelp rating based on user text reviews  &  \href{https://github.com/shahwar9/RatingsPrediction_NLP}{\custombold{Github}}\\
2017   & Shortest Path Solving Server   & \\
2016 	& Autonomous Car Platoon (Fuzzy Logic and Neural Networks)    & \href{https://github.com/shahwar9/AutonomousCarPlatoon/}{\custombold{Github}}
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}